### 2024-09-09 texts/sup_materials.tex
add extra models with AF variables to sup_materials

% Created 2024-09-06 vr 15:46
% Intended LaTeX compiler: pdflatex
\documentclass[12pt]{article}

@@

% latex table generated in R 4.3.3 by xtable 1.8-4 package
% Fri Sep  6 15:29:56 2024
\begin{table}[ht]
\centering
\begin{tabular}{p{0mm}lD{)}{)}{8)3}D{)}{)}{8)3}D{)}{)}{8)3}D{)}{)}{8)3}D{)}{)}{8)3}}
  \hline 
 \multicolumn{1}{l}{} & \multicolumn{1}{l}{Variable} & \multicolumn{1}{l}{r\_pop4} & \multicolumn{1}{l}{r\_pmdens1} & \multicolumn{1}{l}{r\_pmdens2} & \multicolumn{1}{l}{r\_audience1} & \multicolumn{1}{l}{r\_audience\_log1}\\ 
 \hline
  \multicolumn{7}{l}{\textbf{Founder}} \\ 
 & Gender - Female & -.04 \; (0.34) & .00 \; (0.33) & -.05 \; (0.33) & -.00 \; (0.33) & -.11 \; (0.33) \\ 
   & Gender - Couple & -.14 \; (0.32) & -.22 \; (0.32) & -.18 \; (0.32) & -.21 \; (0.32) & -.23 \; (0.32) \\ 
   & Founder died & .28 \; (0.43) & .19 \; (0.43) & .25 \; (0.43) & .18 \; (0.43) & .08 \; (0.43) \\ 
   \multicolumn{7}{l}{\textbf{Museum}} \\ 
 & Self-Identification - Foundation & .20 \; (0.41) & .36 \; (0.40) & .33 \; (0.40) & .37 \; (0.40) & .44 \; (0.40) \\ 
   & Self-Identification - Collection & -.45 \; (0.54) & -.09 \; (0.50) & -.20 \; (0.51) & -.05 \; (0.51) & .05 \; (0.51) \\ 
   & Self-Identification - Other & 1.09 \; (0.30)^{***} & 1.03 \; (0.30)^{***} & 1.12 \; (0.31)^{***} & 1.05 \; (0.30)^{***} & 1.13 \; (0.30)^{***} \\ 
   & AN Ranking - Included & .19 \; (0.34) & .24 \; (0.34) & .17 \; (0.35) & .23 \; (0.34) & .18 \; (0.34) \\ 
   & AN Ranking - Dropped & .46 \; (0.50) & .45 \; (0.50) & .31 \; (0.50) & .45 \; (0.49) & .47 \; (0.49) \\ 
   & Founder name in Museum name & .05 \; (0.28) & .10 \; (0.28) & .14 \; (0.28) & .10 \; (0.28) & .07 \; (0.28) \\ 
   \multicolumn{7}{l}{\textbf{Environment}} \\ 
 & PM density (country) & .65 \; (0.34) & .50 \; (0.32) & .41 \; (0.34) & .55 \; (0.33) & .73 \; (0.31)^{*} \\ 
   & PM density$^{2}$ (country) & -.03 \; (0.02) & -.02 \; (0.02) & -.02 \; (0.02) & -.02 \; (0.02) & -.03 \; (0.03) \\ 
   & Pop. (millions) within 10km & .27 \; (0.09)^{**} &  &  &  &  \\ 
   & Nbr PM within 10km & .26 \; (0.08)^{***} &  &  &  &  \\ 
   & PM density (10km) &  & -.00 \; (0.03) &  &  &  \\ 
   & PM density (10km, log) &  &  & .29 \; (0.15) &  &  \\ 
   & Nbr PM (10km) * Pop (10km) & -.09 \; (0.03)^{**} &  &  &  &  \\ 
   & Local Audience per PM &  &  &  & .10 \; (0.14) &  \\ 
   & Local Audience per PM (log) &  &  &  &  & .28 \; (0.09)^{**} \\ 
   & Great Recession (2008/09) & -1.59 \; (1.01) & -1.65 \; (1.01) & -1.64 \; (1.01) & -1.65 \; (1.01) & -1.63 \; (1.01) \\ 
   & Covid Pandemic (2020/21) & .42 \; (0.29) & .44 \; (0.29) & .46 \; (0.29) & .43 \; (0.29) & .42 \; (0.29) \\ 
   \hline
 & Museums & 503 & 503 & 503 & 503 & 503 \\ 
   & Museum-years & 6096 & 6096 & 6096 & 6096 & 6096 \\ 
   & Closures & 68 & 68 & 68 & 68 & 68 \\ 
   & log. Likelihood & -339.68 & -347.93 & -346.18 & -347.72 & -342.93 \\ 
   & AIC & 711.35 & 723.85 & 720.35 & 723.44 & 713.86 \\ 
   & BIC & 746.87 & 754.93 & 751.42 & 754.51 & 744.93 \\ 
   \hline 
 \multicolumn{7}{l}{\footnotesize{standard errors in parantheses.\textsuperscript{***}p $<$ 0.001;\textsuperscript{**}p $<$ 0.01;\textsuperscript{*}p $<$ 0.05.}}
\end{tabular}
\caption{Alternative specification of environment} 
\label{tbl:t_reg_coxph_env}
\end{table}

@@

@@

% latex table generated in R 4.3.3 by xtable 1.8-4 package
% Fri Sep  6 15:29:49 2024
\begin{table}[ht]
\centering
\begin{tabular}{p{0mm}lD{)}{)}{8)3}D{)}{)}{8)3}D{)}{)}{8)3}D{)}{)}{8)3}}
  \hline 
 \multicolumn{1}{l}{} & \multicolumn{1}{l}{Variable} & \multicolumn{1}{l}{r\_pop4} & \multicolumn{1}{l}{r\_onlycryside} & \multicolumn{1}{l}{r\_wocryside} & \multicolumn{1}{l}{r\_pop42}\\ 
 \hline
  \multicolumn{6}{l}{\textbf{Founder}} \\ 
 & Gender - Female & -.04 \; (0.34) & -1.07 \; (0.78) & .21 \; (0.44) & -.01 \; (0.34) \\ 
   & Gender - Couple & -.14 \; (0.32) & -.27 \; (0.46) & .07 \; (0.52) & -.12 \; (0.32) \\ 
   & Founder died & .28 \; (0.43) & .58 \; (0.59) & -.19 \; (0.77) & .29 \; (0.43) \\ 
   \multicolumn{6}{l}{\textbf{Museum}} \\ 
 & Self-Identification - Foundation & .20 \; (0.41) & .31 \; (0.58) & 1.02 \; (0.65) & .18 \; (0.41) \\ 
   & Self-Identification - Collection & -.45 \; (0.54) & -18.23 \; (4781.88) & .95 \; (0.71) & -.50 \; (0.55) \\ 
   & Self-Identification - Other & 1.09 \; (0.30)^{***} & .67 \; (0.46) & 1.95 \; (0.51)^{***} & 1.09 \; (0.31)^{***} \\ 
   & AN Ranking - Included & .19 \; (0.34) & .55 \; (0.58) & -.32 \; (0.48) & .18 \; (0.34) \\ 
   & AN Ranking - Dropped & .46 \; (0.50) & -.06 \; (0.85) & .18 \; (0.73) & .47 \; (0.50) \\ 
   & Founder name in Museum name & .05 \; (0.28) & .24 \; (0.44) & -.30 \; (0.42) & .04 \; (0.28) \\ 
   \multicolumn{6}{l}{\textbf{Environment}} \\ 
 & PM density (country) & .65 \; (0.34) & .88 \; (0.44)^{*} & -1.16 \; (2.52) & .67 \; (0.34)^{*} \\ 
   & PM density$^{2}$ (country) & -.03 \; (0.02) & -.04 \; (0.02) & 1.33 \; (2.38) & -.03 \; (0.02) \\ 
   & Pop. (millions) within 10km & .27 \; (0.09)^{**} & 1.69 \; (0.81)^{*} & .17 \; (0.17) & .20 \; (0.12) \\ 
   & Nbr PM within 10km & .26 \; (0.08)^{***} & .64 \; (1.06) & .19 \; (0.10) & .22 \; (0.20) \\ 
   & Nbr PM$^{2}$ within 10km &  &  &  & .01 \; (0.02) \\ 
   & Nbr PM (10km) * Pop (10km) & -.09 \; (0.03)^{**} & -.54 \; (1.83) & -.07 \; (0.04)^{*} & -.02 \; (0.09) \\ 
   & Nbr PM$^{2}$ (10km) * Pop (10km) &  &  &  & -.01 \; (0.01) \\ 
   & Great Recession (2008/09) & -1.59 \; (1.01) & -.75 \; (1.04) & -18.42 \; (5245.29) & -1.59 \; (1.01) \\ 
   & Covid Pandemic (2020/21) & .42 \; (0.29) & .46 \; (0.47) & .30 \; (0.41) & .45 \; (0.29) \\ 
   \hline
 & Museums & 503 & 283 & 219 & 503 \\ 
   & Museum-years & 6096 & 3311 & 2265 & 6096 \\ 
   & Closures & 68 & 28 & 35 & 68 \\ 
   & log. Likelihood & -339.68 & -116.47 & -139.36 & -338.79 \\ 
   & AIC & 711.35 & 264.94 & 310.72 & 713.59 \\ 
   & BIC & 746.87 & 286.25 & 335.60 & 753.54 \\ 
   \hline 
 \multicolumn{6}{l}{\footnotesize{standard errors in parantheses.\textsuperscript{***}p $<$ 0.001;\textsuperscript{**}p $<$ 0.01;\textsuperscript{*}p $<$ 0.05.}}
\end{tabular}
\caption{Cox PH models of different local density specifications} 
\label{tbl:t_reg_coxph_density}
\end{table}

@@

% latex table generated in R 4.3.3 by xtable 1.8-4 package
% Fri Sep  6 15:29:50 2024
\begin{table}[ht]
\centering
\begin{tabular}{p{0mm}lD{)}{)}{8)3}D{)}{)}{8)3}D{)}{)}{8)3}D{)}{)}{8)3}}
  \hline 
 \multicolumn{1}{l}{} & \multicolumn{1}{l}{Variable} & \multicolumn{1}{l}{r\_pop4} & \multicolumn{1}{l}{r\_2005} & \multicolumn{1}{l}{r\_2010} & \multicolumn{1}{l}{r\_2015}\\ 
 \hline
  \multicolumn{6}{l}{\textbf{Founder}} \\ 
 & Gender - Female & -.04 \; (0.34) & .00 \; (0.34) & .05 \; (0.34) & .31 \; (0.37) \\ 
   & Gender - Couple & -.14 \; (0.32) & -.10 \; (0.32) & -.39 \; (0.35) & -.35 \; (0.40) \\ 
   & Founder died & .28 \; (0.43) & .13 \; (0.46) & .34 \; (0.46) & -.22 \; (0.55) \\ 
   \multicolumn{6}{l}{\textbf{Museum}} \\ 
 & Self-Identification - Foundation & .20 \; (0.41) & .25 \; (0.42) & .24 \; (0.43) & -.13 \; (0.48) \\ 
   & Self-Identification - Collection & -.45 \; (0.54) & -.41 \; (0.54) & -.37 \; (0.55) & -.62 \; (0.60) \\ 
   & Self-Identification - Other & 1.09 \; (0.30)^{***} & 1.14 \; (0.31)^{***} & 1.15 \; (0.32)^{***} & .96 \; (0.35)^{**} \\ 
   & AN Ranking - Included & .19 \; (0.34) & .17 \; (0.34) & .26 \; (0.35) & -.35 \; (0.49) \\ 
   & AN Ranking - Dropped & .46 \; (0.50) & .22 \; (0.55) & .28 \; (0.55) & .13 \; (0.56) \\ 
   & Founder name in Museum name & .05 \; (0.28) & .05 \; (0.28) & -.01 \; (0.29) & .46 \; (0.32) \\ 
   \multicolumn{6}{l}{\textbf{Environment}} \\ 
 & PM density (country) & .65 \; (0.34) & .70 \; (0.38) & .40 \; (0.45) & .25 \; (0.51) \\ 
   & PM density$^{2}$ (country) & -.03 \; (0.02) & -.03 \; (0.02) & -.02 \; (0.03) & -.02 \; (0.06) \\ 
   & Pop. (millions) within 10km & .27 \; (0.09)^{**} & .27 \; (0.10)^{**} & .25 \; (0.10)^{**} & .24 \; (0.11)^{*} \\ 
   & Nbr PM within 10km & .26 \; (0.08)^{***} & .25 \; (0.08)^{***} & .25 \; (0.08)^{***} & .23 \; (0.08)^{**} \\ 
   & Nbr PM (10km) * Pop (10km) & -.09 \; (0.03)^{**} & -.09 \; (0.03)^{**} & -.09 \; (0.03)^{**} & -.07 \; (0.03)^{*} \\ 
   & Great Recession (2008/09) & -1.59 \; (1.01) & -1.69 \; (1.01) &  &  \\ 
   & Covid Pandemic (2020/21) & .42 \; (0.29) & .33 \; (0.29) & .28 \; (0.30) & .12 \; (0.31) \\ 
   \hline
 & Museums & 503 & 502 & 499 & 485 \\ 
   & Museum-years & 6096 & 5483 & 4474 & 2901 \\ 
   & Closures & 68 & 67 & 64 & 50 \\ 
   & log. Likelihood & -339.68 & -329.47 & -304.28 & -217.32 \\ 
   & AIC & 711.35 & 690.94 & 638.57 & 464.65 \\ 
   & BIC & 746.87 & 726.22 & 670.95 & 493.33 \\ 
   \hline 
 \multicolumn{6}{l}{\footnotesize{standard errors in parantheses.\textsuperscript{***}p $<$ 0.001;\textsuperscript{**}p $<$ 0.01;\textsuperscript{*}p $<$ 0.05.}}
\end{tabular}
\caption{Cox PH regression results with different time slices} 
\label{tbl:t_reg_coxph_timeslice}
\end{table}

Table \ref{tbl:t_reg_coxph_timecfg} investigates whether relationships have substantially changed over time.
However, subsetting the dataset to different year ranges shows general consistency of the main findings, in particular insignificant coefficients for the founder's death, gender, Artnews ranking variables, inclusion of founder name in museum name, positive and significant coefficients for self-identification as other, population and private museum numbers, and a significant negative interaction between private museum numbers and population.
\end{document}

>>>>

% Created 2024-09-09 ma 11:38
% Intended LaTeX compiler: pdflatex
\documentclass[12pt]{article}

@@

@@

\begin{landscape}
% latex table generated in R 4.3.3 by xtable 1.8-4 package
% Fri Sep  6 15:49:47 2024
\begin{table}[ht]
\centering
\begin{tabular}{p{0mm}lD{)}{)}{8)3}D{)}{)}{8)3}D{)}{)}{8)3}D{)}{)}{8)3}D{)}{)}{8)3}}
  \hline 
 \multicolumn{1}{l}{} & \multicolumn{1}{l}{Variable} & \multicolumn{1}{l}{r\_pop4} & \multicolumn{1}{l}{r\_pmdens1} & \multicolumn{1}{l}{r\_pmdens2} & \multicolumn{1}{l}{r\_audience1} & \multicolumn{1}{l}{r\_audience\_log1}\\ 
 \hline
  \multicolumn{7}{l}{\textbf{Founder}} \\ 
 & Gender - Female & -.04 \; (0.34) & .00 \; (0.33) & -.05 \; (0.33) & -.00 \; (0.33) & -.11 \; (0.33) \\ 
   & Gender - Couple & -.14 \; (0.32) & -.22 \; (0.32) & -.18 \; (0.32) & -.21 \; (0.32) & -.23 \; (0.32) \\ 
   & Founder died & .28 \; (0.43) & .19 \; (0.43) & .25 \; (0.43) & .18 \; (0.43) & .08 \; (0.43) \\ 
   \multicolumn{7}{l}{\textbf{Museum}} \\ 
 & Self-Identification - Foundation & .20 \; (0.41) & .36 \; (0.40) & .33 \; (0.40) & .37 \; (0.40) & .44 \; (0.40) \\ 
   & Self-Identification - Collection & -.45 \; (0.54) & -.09 \; (0.50) & -.20 \; (0.51) & -.05 \; (0.51) & .05 \; (0.51) \\ 
   & Self-Identification - Other & 1.09 \; (0.30)^{***} & 1.03 \; (0.30)^{***} & 1.12 \; (0.31)^{***} & 1.05 \; (0.30)^{***} & 1.13 \; (0.30)^{***} \\ 
   & AN Ranking - Included & .19 \; (0.34) & .24 \; (0.34) & .17 \; (0.35) & .23 \; (0.34) & .18 \; (0.34) \\ 
   & AN Ranking - Dropped & .46 \; (0.50) & .45 \; (0.50) & .31 \; (0.50) & .45 \; (0.49) & .47 \; (0.49) \\ 
   & Founder name in Museum name & .05 \; (0.28) & .10 \; (0.28) & .14 \; (0.28) & .10 \; (0.28) & .07 \; (0.28) \\ 
   \multicolumn{7}{l}{\textbf{Environment}} \\ 
 & PM density (country) & .65 \; (0.34) & .50 \; (0.32) & .41 \; (0.34) & .55 \; (0.33) & .73 \; (0.31)^{*} \\ 
   & PM density$^{2}$ (country) & -.03 \; (0.02) & -.02 \; (0.02) & -.02 \; (0.02) & -.02 \; (0.02) & -.03 \; (0.03) \\ 
   & Pop. (millions) within 10km & .27 \; (0.09)^{**} &  &  &  &  \\ 
   & Nbr PM within 10km & .26 \; (0.08)^{***} &  &  &  &  \\ 
   & PM density (10km) &  & -.00 \; (0.03) &  &  &  \\ 
   & PM density (10km, log) &  &  & .29 \; (0.15) &  &  \\ 
   & Nbr PM (10km) * Pop (10km) & -.09 \; (0.03)^{**} &  &  &  &  \\ 
   & Local Audience per PM &  &  &  & .10 \; (0.14) &  \\ 
   & Local Audience per PM (log) &  &  &  &  & .28 \; (0.09)^{**} \\ 
   & Great Recession (2008/09) & -1.59 \; (1.01) & -1.65 \; (1.01) & -1.64 \; (1.01) & -1.65 \; (1.01) & -1.63 \; (1.01) \\ 
   & Covid Pandemic (2020/21) & .42 \; (0.29) & .44 \; (0.29) & .46 \; (0.29) & .43 \; (0.29) & .42 \; (0.29) \\ 
   \hline
 & Museums & 503 & 503 & 503 & 503 & 503 \\ 
   & Museum-years & 6096 & 6096 & 6096 & 6096 & 6096 \\ 
   & Closures & 68 & 68 & 68 & 68 & 68 \\ 
   & log. Likelihood & -339.68 & -347.93 & -346.18 & -347.72 & -342.93 \\ 
   & AIC & 711.35 & 723.85 & 720.35 & 723.44 & 713.86 \\ 
   & BIC & 746.87 & 754.93 & 751.42 & 754.51 & 744.93 \\ 
   \hline 
 \multicolumn{7}{l}{\footnotesize{standard errors in parantheses.\textsuperscript{***}p $<$ 0.001;\textsuperscript{**}p $<$ 0.01;\textsuperscript{*}p $<$ 0.05.}}
\end{tabular}
\caption{Alternative specification of environment} 
\label{tbl:t_reg_coxph_env}
\end{table}
\end{landscape}

@@

% latex table generated in R 4.3.3 by xtable 1.8-4 package
% Fri Sep  6 15:49:39 2024
\begin{table}[ht]
\centering
\begin{tabular}{p{0mm}lD{)}{)}{8)3}D{)}{)}{8)3}D{)}{)}{8)3}D{)}{)}{8)3}}
  \hline 
 \multicolumn{1}{l}{} & \multicolumn{1}{l}{Variable} & \multicolumn{1}{l}{r\_pop4} & \multicolumn{1}{l}{r\_onlycryside} & \multicolumn{1}{l}{r\_wocryside} & \multicolumn{1}{l}{r\_pop42}\\ 
 \hline
  \multicolumn{6}{l}{\textbf{Founder}} \\ 
 & Gender - Female & -.04 \; (0.34) & -1.07 \; (0.78) & .21 \; (0.44) & -.01 \; (0.34) \\ 
   & Gender - Couple & -.14 \; (0.32) & -.27 \; (0.46) & .07 \; (0.52) & -.12 \; (0.32) \\ 
   & Founder died & .28 \; (0.43) & .58 \; (0.59) & -.19 \; (0.77) & .29 \; (0.43) \\ 
   \multicolumn{6}{l}{\textbf{Museum}} \\ 
 & Self-Identification - Foundation & .20 \; (0.41) & .31 \; (0.58) & 1.02 \; (0.65) & .18 \; (0.41) \\ 
   & Self-Identification - Collection & -.45 \; (0.54) & -18.23 \; (4781.88) & .95 \; (0.71) & -.50 \; (0.55) \\ 
   & Self-Identification - Other & 1.09 \; (0.30)^{***} & .67 \; (0.46) & 1.95 \; (0.51)^{***} & 1.09 \; (0.31)^{***} \\ 
   & AN Ranking - Included & .19 \; (0.34) & .55 \; (0.58) & -.32 \; (0.48) & .18 \; (0.34) \\ 
   & AN Ranking - Dropped & .46 \; (0.50) & -.06 \; (0.85) & .18 \; (0.73) & .47 \; (0.50) \\ 
   & Founder name in Museum name & .05 \; (0.28) & .24 \; (0.44) & -.30 \; (0.42) & .04 \; (0.28) \\ 
   \multicolumn{6}{l}{\textbf{Environment}} \\ 
 & PM density (country) & .65 \; (0.34) & .88 \; (0.44)^{*} & -1.16 \; (2.52) & .67 \; (0.34)^{*} \\ 
   & PM density$^{2}$ (country) & -.03 \; (0.02) & -.04 \; (0.02) & 1.33 \; (2.38) & -.03 \; (0.02) \\ 
   & Pop. (millions) within 10km & .27 \; (0.09)^{**} & 1.69 \; (0.81)^{*} & .17 \; (0.17) & .20 \; (0.12) \\ 
   & Nbr PM within 10km & .26 \; (0.08)^{***} & .64 \; (1.06) & .19 \; (0.10) & .22 \; (0.20) \\ 
   & Nbr PM$^{2}$ within 10km &  &  &  & .01 \; (0.02) \\ 
   & Nbr PM (10km) * Pop (10km) & -.09 \; (0.03)^{**} & -.54 \; (1.83) & -.07 \; (0.04)^{*} & -.02 \; (0.09) \\ 
   & Nbr PM$^{2}$ (10km) * Pop (10km) &  &  &  & -.01 \; (0.01) \\ 
   & Great Recession (2008/09) & -1.59 \; (1.01) & -.75 \; (1.04) & -18.42 \; (5245.29) & -1.59 \; (1.01) \\ 
   & Covid Pandemic (2020/21) & .42 \; (0.29) & .46 \; (0.47) & .30 \; (0.41) & .45 \; (0.29) \\ 
   \hline
 & Museums & 503 & 283 & 219 & 503 \\ 
   & Museum-years & 6096 & 3311 & 2265 & 6096 \\ 
   & Closures & 68 & 28 & 35 & 68 \\ 
   & log. Likelihood & -339.68 & -116.47 & -139.36 & -338.79 \\ 
   & AIC & 711.35 & 264.94 & 310.72 & 713.59 \\ 
   & BIC & 746.87 & 286.25 & 335.60 & 753.54 \\ 
   \hline 
 \multicolumn{6}{l}{\footnotesize{standard errors in parantheses.\textsuperscript{***}p $<$ 0.001;\textsuperscript{**}p $<$ 0.01;\textsuperscript{*}p $<$ 0.05.}}
\end{tabular}
\caption{Cox PH models of different local density specifications} 
\label{tbl:t_reg_coxph_density}
\end{table}

@@

% latex table generated in R 4.3.3 by xtable 1.8-4 package
% Fri Sep  6 15:49:41 2024
\begin{table}[ht]
\centering
\begin{tabular}{p{0mm}lD{)}{)}{8)3}D{)}{)}{8)3}D{)}{)}{8)3}D{)}{)}{8)3}}
  \hline 
 \multicolumn{1}{l}{} & \multicolumn{1}{l}{Variable} & \multicolumn{1}{l}{r\_pop4} & \multicolumn{1}{l}{r\_2005} & \multicolumn{1}{l}{r\_2010} & \multicolumn{1}{l}{r\_2015}\\ 
 \hline
  \multicolumn{6}{l}{\textbf{Founder}} \\ 
 & Gender - Female & -.04 \; (0.34) & .00 \; (0.34) & .05 \; (0.34) & .31 \; (0.37) \\ 
   & Gender - Couple & -.14 \; (0.32) & -.10 \; (0.32) & -.39 \; (0.35) & -.35 \; (0.40) \\ 
   & Founder died & .28 \; (0.43) & .13 \; (0.46) & .34 \; (0.46) & -.22 \; (0.55) \\ 
   \multicolumn{6}{l}{\textbf{Museum}} \\ 
 & Self-Identification - Foundation & .20 \; (0.41) & .25 \; (0.42) & .24 \; (0.43) & -.13 \; (0.48) \\ 
   & Self-Identification - Collection & -.45 \; (0.54) & -.41 \; (0.54) & -.37 \; (0.55) & -.62 \; (0.60) \\ 
   & Self-Identification - Other & 1.09 \; (0.30)^{***} & 1.14 \; (0.31)^{***} & 1.15 \; (0.32)^{***} & .96 \; (0.35)^{**} \\ 
   & AN Ranking - Included & .19 \; (0.34) & .17 \; (0.34) & .26 \; (0.35) & -.35 \; (0.49) \\ 
   & AN Ranking - Dropped & .46 \; (0.50) & .22 \; (0.55) & .28 \; (0.55) & .13 \; (0.56) \\ 
   & Founder name in Museum name & .05 \; (0.28) & .05 \; (0.28) & -.01 \; (0.29) & .46 \; (0.32) \\ 
   \multicolumn{6}{l}{\textbf{Environment}} \\ 
 & PM density (country) & .65 \; (0.34) & .70 \; (0.38) & .40 \; (0.45) & .25 \; (0.51) \\ 
   & PM density$^{2}$ (country) & -.03 \; (0.02) & -.03 \; (0.02) & -.02 \; (0.03) & -.02 \; (0.06) \\ 
   & Pop. (millions) within 10km & .27 \; (0.09)^{**} & .27 \; (0.10)^{**} & .25 \; (0.10)^{**} & .24 \; (0.11)^{*} \\ 
   & Nbr PM within 10km & .26 \; (0.08)^{***} & .25 \; (0.08)^{***} & .25 \; (0.08)^{***} & .23 \; (0.08)^{**} \\ 
   & Nbr PM (10km) * Pop (10km) & -.09 \; (0.03)^{**} & -.09 \; (0.03)^{**} & -.09 \; (0.03)^{**} & -.07 \; (0.03)^{*} \\ 
   & Great Recession (2008/09) & -1.59 \; (1.01) & -1.69 \; (1.01) &  &  \\ 
   & Covid Pandemic (2020/21) & .42 \; (0.29) & .33 \; (0.29) & .28 \; (0.30) & .12 \; (0.31) \\ 
   \hline
 & Museums & 503 & 502 & 499 & 485 \\ 
   & Museum-years & 6096 & 5483 & 4474 & 2901 \\ 
   & Closures & 68 & 67 & 64 & 50 \\ 
   & log. Likelihood & -339.68 & -329.47 & -304.28 & -217.32 \\ 
   & AIC & 711.35 & 690.94 & 638.57 & 464.65 \\ 
   & BIC & 746.87 & 726.22 & 670.95 & 493.33 \\ 
   \hline 
 \multicolumn{6}{l}{\footnotesize{standard errors in parantheses.\textsuperscript{***}p $<$ 0.001;\textsuperscript{**}p $<$ 0.01;\textsuperscript{*}p $<$ 0.05.}}
\end{tabular}
\caption{Cox PH regression results with different time slices} 
\label{tbl:t_reg_coxph_timeslice}
\end{table}

Table \ref{tbl:t_reg_coxph_timeslice} investigates whether relationships have substantially changed over time.
However, subsetting the dataset to different year ranges shows general consistency of the main findings, in particular insignificant coefficients for the founder's death, gender, Artnews ranking variables, inclusion of founder name in museum name, positive and significant coefficients for self-identification as other, population and private museum numbers, and a significant negative interaction between private museum numbers and population.
\subsection*{Inclusion of Exhibition data}

% latex table generated in R 4.3.3 by xtable 1.8-4 package
% Mon Sep  9 11:20:03 2024
\begin{table}[ht]
\centering
\begin{tabular}{p{0mm}lD{)}{)}{8)3}D{)}{)}{8)3}D{)}{)}{8)3}}
  \hline 
 \multicolumn{1}{l}{} & \multicolumn{1}{l}{Variable} & \multicolumn{1}{l}{r\_pop4} & \multicolumn{1}{l}{r\_exhbany} & \multicolumn{1}{l}{r\_exhbroll}\\ 
 \hline
  \multicolumn{5}{l}{\textbf{Founder}} \\ 
 & Gender - Female & -.04 \; (0.34) & -.01 \; (0.34) & -.06 \; (0.34) \\ 
   & Gender - Couple & -.14 \; (0.32) & -.12 \; (0.32) & -.15 \; (0.32) \\ 
   & Founder died & .28 \; (0.43) & .31 \; (0.43) & .26 \; (0.43) \\ 
   \multicolumn{5}{l}{\textbf{Museum}} \\ 
 & Self-Identification - Foundation & .20 \; (0.41) & .24 \; (0.42) & .17 \; (0.41) \\ 
   & Self-Identification - Collection & -.45 \; (0.54) & -.47 \; (0.55) & -.42 \; (0.54) \\ 
   & Self-Identification - Other & 1.09 \; (0.30)^{***} & 1.13 \; (0.31)^{***} & 1.07 \; (0.30)^{***} \\ 
   & AN Ranking - Included & .19 \; (0.34) & .26 \; (0.36) & .13 \; (0.35) \\ 
   & AN Ranking - Dropped & .46 \; (0.50) & .50 \; (0.50) & .42 \; (0.50) \\ 
   & Founder name in Museum name & .05 \; (0.28) & .07 \; (0.28) & .03 \; (0.28) \\ 
   & Exhibition any &  & -.22 \; (0.27) &  \\ 
   & Exhibition any last 5 years &  &  & .20 \; (0.26) \\ 
   \multicolumn{5}{l}{\textbf{Environment}} \\ 
 & PM density (country) & .65 \; (0.34) & .66 \; (0.35) & .65 \; (0.35) \\ 
   & PM density$^{2}$ (country) & -.03 \; (0.02) & -.03 \; (0.02) & -.03 \; (0.02) \\ 
   & Pop. (millions) within 10km & .27 \; (0.09)^{**} & .27 \; (0.09)^{**} & .27 \; (0.10)^{**} \\ 
   & Nbr PM within 10km & .26 \; (0.08)^{***} & .26 \; (0.08)^{***} & .27 \; (0.08)^{***} \\ 
   & Nbr PM (10km) * Pop (10km) & -.09 \; (0.03)^{**} & -.09 \; (0.03)^{**} & -.09 \; (0.03)^{**} \\ 
   & Great Recession (2008/09) & -1.59 \; (1.01) & -1.60 \; (1.01) & -1.57 \; (1.01) \\ 
   & Covid Pandemic (2020/21) & .42 \; (0.29) & .42 \; (0.29) & .41 \; (0.29) \\ 
   \hline
 & Museums & 503 & 503 & 503 \\ 
   & Museum-years & 6096 & 6096 & 6096 \\ 
   & Closures & 68 & 68 & 68 \\ 
   & log. Likelihood & -339.68 & -339.34 & -339.38 \\ 
   & AIC & 711.35 & 712.67 & 712.76 \\ 
   & BIC & 746.87 & 750.41 & 750.50 \\ 
   \hline 
 \multicolumn{5}{l}{\footnotesize{standard errors in parantheses.\textsuperscript{***}p $<$ 0.001;\textsuperscript{**}p $<$ 0.01;\textsuperscript{*}p $<$ 0.05.}}
\end{tabular}
\caption{Alternative specification: include Exhibition} 
\label{tbl:t_reg_coxph_af}
\end{table}

It is also possible to include an indicator whether museums have had exhibitions of contemporary art.
For this the database of Artfacts is used.
It is not included in the main model as it might reflect resources (with larger museums being more likely to organize exhibitions), which would then influence the coefficients of other variables. 
Controlling for the mechanism (or a proxy of it) would then lead to coefficients corresponding to comparisons where resources are equal.
To investigate the role of exhibitions anyways, table \ref{tbl:t_reg_coxph_af} includes next to the main model two models with different exhibition specifications.
"Exhibition any" is a time-invariant indicator measuring whether Artfacts has ever recorded this museum as organizating an exhibition, "Exhibition any last 5 years" is a time-varying variable indicating whether an exhibition has been taken place in the previous 5 years.
Both coefficients are not significant, and do not substantially change the coefficients of other variables. 
\end{document}
